---
title: "03_dynamic_filter"
author: "Cristian E. Nuno"
date: "4/8/2020"
output: html_document
---

# Purpose

This RMarkdown demonstrates how to import a separate `.R` file that a function you would like use in this RMarkdown file.

```{r, message=FALSE}
# load necessary packages
library(dplyr)
library(here)
library(pander)

# load necessary data
iris_df <- iris
```

## Source `.R` files

Storing `.R` code in a separate file is good practice when you would like to safely partition logic away from the analysis displayed to the audience while still showing them where it originates from. 

The [`source()`](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/source) will execute the `.R` script and make all objects available to you in your current Global Environment.

```{r}
# load functions
source(here("R/analysis/functions/dynamic_filter.R"))
```

## Use the newly imported `filter_df()` function

```{r}
# use the function to create a new data frame
iris_filter_df <-
  filter_df(df=iris_df, keyword="setosa", column_name="Species")

# display the results
pander(head(iris_filter_df))
```

